Using physical simulations to predict children's and adults' preferences in physical interactions

### 2021-02-03 paper/paper2021.Rmd
paper stuff

---
# Mike has a better title git stashed but G can't remember it..
# old: What if you drop that? Developmental changes in curiosity about physical interactions
title: "Using physical simulations to predict children's and adults' preference for physical interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

abstract: >
     Curiosity is a fundamental driver of human behavior, and yet because of its open-ended nature 
     and the wide variety of behaviors it inspires in different contexts, it is remarkably difficult 
     to study in a laboratory context. A promising approach to developing and testing theories of 
     curiosity is to instantiate them in artificial agents that are able to act and explore in a 
     simulated environment, and then compare the behavior of these agents to humans exploring the 
     same stimuli. Here we propose a new experimental paradigm for examining children's--and 
     AI agents'--curiosity about objects' physical interactions by letting them choose which object to 
     target when dropping a given object. We compared adults' (N=155) and children's choices (N=66; 
     3-7 year-olds) and found that adults show a strong preference for choices affording a containment
     relation, a preference that is also shown by children. Adults alone also make choices consistent 
     with achieving support relations. We contextualize our results using heuristic models based on 
     physics simulations of the same scenarios judged by participants.

@@

Curiosity is a hallmark aspect of human intelligence. 
From infants exploring the objects in their environment to scientists exploring the frontiers of our solar system, humans are highly motivated to seek out new knowledge and experiences. 
However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009; @Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015]. 
Moreover, extant theories have rarely provided quantitatively precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans.

>>>>

---
# Mike has a better title git stashed but G can't remember it..
# old: What if you drop that? Developmental changes in curiosity about physical interactions
title: "Using physical simulations to predict children's and adults' preferences in physical interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

abstract: >
     Curiosity is a fundamental driver of human behavior, and yet because of its open-ended nature 
     and the wide variety of behaviors it inspires in different contexts, it is remarkably difficult 
     to study in a laboratory context. A promising approach to developing and testing theories of 
     curiosity is to instantiate them in artificial agents that are able to act and explore in a 
     simulated environment, and then compare the behavior of these agents to humans exploring the 
     same stimuli. Here we propose a new experimental paradigm for examining children's -- and 
     AI agents' -- curiosity about objects' physical interactions.
     We let them choose which object to 
     drop another object onto in order to create the most interesting effect. We compared adults' (N=155) and children's choices (N=66; 
     3-7 year-olds) and found that adults show a strong preference for drops that could potentially result in a containment
     relation, a preference that is also shown by children. Adults alone also make choices consistent 
     with achieving support relations. We contextualize our results using heuristic computational models based on 
     3D physical simulations of the same scenarios judged by participants.

@@

Curiosity is a hallmark aspect of human intelligence. 
From infants exploring the objects in their environment to scientists exploring the frontiers of our solar system, humans are highly motivated to seek out new knowledge and experiences. 
Although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009; @Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015]. 
Moreover, extant theories have rarely provided precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans, in part because curiosity tends to result in complex, open-ended behaviors that are difficult to quantify.
